\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[spanish,english]{babel}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{setspace}

\geometry{top=1in, bottom=1in, left=1in, right=1in}

% Headers and Footers
\pagestyle{fancy}
\fancyhf{}
\lhead{English Exam}
\rhead{Page \thepage}
\lfoot{University of Central Venezuela}
\rfoot{Date: \underline{\hspace{3cm}}}

\titleformat{\section}{\large\bfseries}{}{0em}{}
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    {\huge \textbf{English Exam}} \\
    \vspace{0.5cm}
    \textbf{Name:} \underline{\hspace{8cm}} \quad \textbf{ID:} \underline{\hspace{4cm}}
\end{center}

\vspace{0.3cm}

\begin{tcolorbox}[colback=gray!5,colframe=gray!50,title=Course Objectives \& Evaluation Goals]
    The main objective of this evaluation is to assess the student's proficiency in the English language within a technical and academic context. Specifically, the student should:
    \begin{itemize}[noitemsep]
        \item Demonstrate reading comprehension of complex and scientific texts.
        \item Correctness in the use of advanced grammar (Perfect Tenses, Conditionals, Gerunds).
        \item Accurate translation of technical phrases from English to Spanish.
        \item Vocabulary mastery, including homophones and phrasal verbs.
        \item Ability to draft a coherent academic composition of 160+ words.
    \end{itemize}
\end{tcolorbox}

\vspace{0.5cm}

\section{I. READING COMPREHENSION (10 points)}

\subsection{A. Read through the text and then do the multiple choice exercise.}

\begin{center}
    \textbf{THE PEACELIKE MONGOOSE}
\end{center}

In cobra country a mongoose was born one day who didn't want to fight cobras or anything else. The word spread from mongoose to mongoose that there was a mongoose that didn't want to fight cobras. If he didn't want to fight anything else, it was his own business, but it was the duty of every mongoose to kill cobras or be killed by cobras.

"Why?" asked the peacelike mongoose, and the word went round that the strange new mongoose was not only pro-cobra and anti-mongoose but intellectually curious and against the ideals and traditions of mongoosism.

"He is crazy," cried the young mongoose's father. \\
"He's sick," said his mother, \\
"He is a coward," shouted his brothers. \\
"He's a mongoosexual," whispered his sisters.

Strangers who never had laid eyes on the peacelike mongoose remembered that they had seen him crawling on his stomach, or trying cobra hoods, or plotting the violent overthrow of Mongoodia.

"I'm trying to use reason and intelligence," said the strange new mongoose. \\
"Reason is six-sevenths of treason," said one of his neighbours. \\
"Intelligence is what the enemy uses," said another.

Finally the rumour spread that the mongoose had venom in his sting, like a cobra, and he was tried, convicted by a show of paws, and condemned to banishment.

\vspace{0.3cm}
\textit{Moral: Ashes to ashes, and clay to clay, if the enemy doesn't get you your own folks may.}
\vspace{0.5cm}

\begin{enumerate}
    \item Cobras and mongooses are animals who
    \begin{enumerate}[label=\alph*.]
        \item get along well with each other.
        \item live peacefully side by side.
        \item wage war against each other.
    \end{enumerate}

    \item "Convict" and "condemn" belong to the vocabulary of
    \begin{enumerate}[label=\alph*.]
        \item religion.
        \item politics.
        \item justice.
    \end{enumerate}

    \item The word "spread" suggests that
    \begin{enumerate}[label=\alph*.]
        \item they all told each other the news.
        \item no mongoose was interested in the event.
        \item the news was kept secret.
    \end{enumerate}

    \item "Reason is six-sevenths of treason" implies that
    \begin{enumerate}[label=\alph*.]
        \item the neighbour was only interested in how the words sounded.
        \item you can always create new words by adding a letter.
        \item by using reason the peacelike mongoose is very close to being a traitor to his own folks.
    \end{enumerate}

    \item In this story, the following events take place:
    \begin{enumerate}[label=\arabic*.]
        \item the strange mongoose is convicted.
        \item the strange mongoose refuses to fight cobras.
        \item his family turns against him.
        \item he is banished from the country.
        \item strangers accuse him of being sold to the enemy.
    \end{enumerate}
    The order of events is:
    \begin{enumerate}[label=\alph*.]
        \item 1 2 3 4 5
        \item 3 1 2 5 4
        \item 2 3 5 1 4
    \end{enumerate}

    \item What does not belong to the ideals and traditions of mongoosism?
    \begin{enumerate}[label=\alph*.]
        \item being brave.
        \item killing cobras.
        \item using reason and intelligence.
    \end{enumerate}

    \item "Plotting the overthrow" suggests
    \begin{enumerate}[label=\alph*.]
        \item conspiring against the existing government.
        \item accepting the present state of affairs.
        \item agreeing with the present leaders' policy.
    \end{enumerate}

    \item "Had never laid eyes" means
    \begin{enumerate}[label=\alph*.]
        \item hadn't seen him before.
        \item had been watching him for a longtime.
        \item had already seen him.
    \end{enumerate}

    \item A coward is a person
    \begin{enumerate}[label=\alph*.]
        \item who can easily control his fear.
        \item who is not courageous.
        \item who likes to fight.
    \end{enumerate}

    \item The story and its moral
    \begin{enumerate}[label=\alph*.]
        \item are purely fictional and have no symbolical meaning.
        \item can only apply to the world of cobras and mongooses.
        \item are meant to reflect the relationships among human beings.
    \end{enumerate}

    \item Choose the words in the right list with its synonym: \\
    Paw: \underline{\hspace{3cm}} Sting: \underline{\hspace{3cm}} \\
    Banishment: \underline{\hspace{3cm}} Peacelike: \underline{\hspace{3cm}} \\
    Clay: \underline{\hspace{3cm}} Whispered: \underline{\hspace{3cm}} \\
    Duty: \underline{\hspace{3cm}} Treason: \underline{\hspace{3cm}}
\end{enumerate}

\section{II. HIV BREAKTHROUGH (10 points)}

\subsection{B. Read through the text. Then fill in the blanks using the best option from each item in the multiple choice exercise below.}

Scientists believe that they have made a \underline{\hspace{2cm}} (1) breakthrough in fighting HIV - they have shown what happens when an infection fighting antibody attacks a \underline{\hspace{2cm}} (2) in HIV's \underline{\hspace{2cm}} (3) defences. Finding a vaccine against HIV has been very difficult because the proteins on the surface of the virus are continually mutating, but they have shown an antibody, called b12, attacking a weak spot on the virus where the protein is \underline{\hspace{2cm}} (4). The virus is able to \underline{\hspace{2cm}} (5) rapidly to avoid \underline{\hspace{2cm}} (6) by the immune system, and is also covered in sugary molecules which block access by antibodies. \underline{\hspace{2cm}} (7), certain parts of the virus must remain \underline{\hspace{2cm}} (8) unchanged so that it can catch hold of and enter human cells.

One protein that sticks out from the surface of the virus and binds to receptors on host cells is one such region, which makes it a target for vaccine development.

Previous analyses of the \underline{\hspace{2cm}} (9) of people that have been able to keep HIV from developing into AIDS for long periods of time \underline{\hspace{2cm}} (10) revealed a \underline{\hspace{2cm}} (11) group of antibodies - including b12 - that seem to fight HIV with some degree of \underline{\hspace{2cm}} (12).

\vspace{0.5cm}

\section{III. GRAMMAR (25 points)}

\subsection{C. Choose the best answer for the following sentences:}

\begin{enumerate}
    \item The train \underline{\hspace{2cm}} left.
    \begin{enumerate}[label=\alph*.] \item Has \item Have \end{enumerate}

    \item "I've been here \underline{\hspace{2cm}} Monday."
    \begin{enumerate}[label=\alph*.] \item Since \item For \end{enumerate}

    \item "I looked \underline{\hspace{2cm}} my wallet everywhere."
    \begin{enumerate}[label=\alph*.] \item For \item Off \end{enumerate}

    \item "\underline{\hspace{2cm}} the plane lands, I'll give you a call."
    \begin{enumerate}[label=\alph*.] \item On \item As soon as \end{enumerate}

    \item "Put on the jackets. Put \underline{\hspace{2cm}} on."
    \begin{enumerate}[label=\alph*.] \item Them \item It \end{enumerate}

    \item "This is the man \underline{\hspace{2cm}} bought the package."
    \begin{enumerate}[label=\alph*.] \item Who \item What \end{enumerate}

    \item "Oscar's whole family play tennis but Oscar plays the \underline{\hspace{2cm}}."
    \begin{enumerate}[label=\alph*.] \item Better \item Best \end{enumerate}

    \item "The movie \underline{\hspace{2cm}} started when we got to the theater."
    \begin{enumerate}[label=\alph*.] \item Had \item Have \end{enumerate}

    \item "\underline{\hspace{2cm}} 1975 my grandfather had brought his entire family to Venezuela."
    \begin{enumerate}[label=\alph*.] \item By \item On \end{enumerate}

    \item "The plane had \underline{\hspace{2cm}} landed."
    \begin{enumerate}[label=\alph*.] \item Already \item So \end{enumerate}

    \item "People enjoy \underline{\hspace{2cm}} in cities."
    \begin{enumerate}[label=\alph*.] \item Living \item To live \end{enumerate}

    \item "I suggest \underline{\hspace{2cm}} the bus instead the subway."
    \begin{enumerate}[label=\alph*.] \item To take \item Taking \end{enumerate}

    \item "Alejandro refused \underline{\hspace{2cm}}."
    \begin{enumerate}[label=\alph*.] \item To leave \item Leaving \end{enumerate}

    \item "It's so hot today. I feel \underline{\hspace{2cm}} going swimming."
    \begin{enumerate}[label=\alph*.] \item Like \item On \end{enumerate}

    \item "Camila looks like her father. She takes \underline{\hspace{2cm}} him in so many ways, too."
    \begin{enumerate}[label=\alph*.] \item After \item Like \end{enumerate}

    \item "We can't go out tonight unless we find someone to look \underline{\hspace{2cm}} the children."
    \begin{enumerate}[label=\alph*.] \item Like \item After \end{enumerate}

    \item "Caty will stay in the apartment \underline{\hspace{2cm}} I get back."
    \begin{enumerate}[label=\alph*.] \item Until \item On \end{enumerate}

    \item "I was never good at solving math problems. Solving means:"
    \begin{enumerate}[label=\alph*.] \item Work on \item Work out \end{enumerate}

    \item "Francisco went back after \underline{\hspace{2cm}} lunch."
    \begin{enumerate}[label=\alph*.] \item To eat \item Eating \end{enumerate}

    \item "Gloria insisted \underline{\hspace{2cm}} doing the dishes."
    \begin{enumerate}[label=\alph*.] \item In \item On \end{enumerate}

    \item "I can't make \underline{\hspace{2cm}} my mind whether to go to France or Italy for my vacation."
    \begin{enumerate}[label=\alph*.] \item Off \item Up \end{enumerate}

    \item "If I study English, I \underline{\hspace{2cm}} pass the test."
    \begin{enumerate}[label=\alph*.] \item Will \item Would \end{enumerate}

    \item "The package has \underline{\hspace{2cm}} mailed."
    \begin{enumerate}[label=\alph*.] \item Been \item Being \end{enumerate}

    \item "If I had a car, I \underline{\hspace{2cm}} visit you."
    \begin{enumerate}[label=\alph*.] \item Would \item Will \end{enumerate}

    \item "They regret \underline{\hspace{2cm}} bought the house."
    \begin{enumerate}[label=\alph*.] \item Having \item To have been \end{enumerate}

    \item "If I \underline{\hspace{2cm}} you, I'd be more careful."
    \begin{enumerate}[label=\alph*.] \item Am \item Were \end{enumerate}

    \item "We have finished the job. The job \underline{\hspace{2cm}} been finished."
    \begin{enumerate}[label=\alph*.] \item Have \item Has \end{enumerate}

    \item "Perform\underline{\hspace{2cm}}"
    \begin{enumerate}[label=\alph*.] \item Ant \item Ance \end{enumerate}

    \item "I had the mechanic \underline{\hspace{2cm}} my car."
    \begin{enumerate}[label=\alph*.] \item Repair \item Repaired \end{enumerate}

    \item "I had my car \underline{\hspace{2cm}}"
    \begin{enumerate}[label=\alph*.] \item Repaired \item Repair \end{enumerate}

    \item "I asked you \underline{\hspace{2cm}}"
    \begin{enumerate}[label=\alph*.] \item To come \item Come \end{enumerate}

    \item "Every one jumped from the quickly \underline{\hspace{2cm}} ship."
    \begin{enumerate}[label=\alph*.] \item Sink \item Sinking \end{enumerate}

    \item "We \underline{\hspace{2cm}} have finished our project by next June."
    \begin{enumerate}[label=\alph*.] \item Had \item Will \end{enumerate}

    \item "Years ago, I used to \underline{\hspace{2cm}} in Barcelona."
    \begin{enumerate}[label=\alph*.] \item Live \item Living \end{enumerate}

    \item "I am used to \underline{\hspace{2cm}} in New York."
    \begin{enumerate}[label=\alph*.] \item Living \item Live \end{enumerate}

    \item "Nancy went to lunch. So \underline{\hspace{2cm}} Julio."
    \begin{enumerate}[label=\alph*.] \item Do \item Did \end{enumerate}

    \item "The computers don't work. Neither \underline{\hspace{2cm}} the lamp."
    \begin{enumerate}[label=\alph*.] \item Does \item Do \end{enumerate}

    \item "You are my friend, \underline{\hspace{2cm}} you?"
    \begin{enumerate}[label=\alph*.] \item Are \item Aren't \end{enumerate}

    \item "Paul said 'I need the money'."
    \begin{enumerate}[label=\alph*.] 
        \item Paul said that he need the money.
        \item Paul said that he needed the money.
    \end{enumerate}

    \item He is thought \underline{\hspace{2cm}} intelligent.
    \begin{enumerate}[label=\alph*.] \item To be \item Be \end{enumerate}

    \item If I had arrived on time, I \underline{\hspace{2cm}} not have missed the train.
    \begin{enumerate}[label=\alph*.] \item Will \item Would \end{enumerate}

    \item You suggest that you \underline{\hspace{2cm}} on time.
    \begin{enumerate}[label=\alph*.] \item To be \item Be \end{enumerate}

    \item I \underline{\hspace{2cm}} a mistake.
    \begin{enumerate}[label=\alph*.] \item Make \item Do \end{enumerate}

    \item You \underline{\hspace{2cm}} your homework.
    \begin{enumerate}[label=\alph*.] \item Make \item Do \end{enumerate}

    \item I wish I \underline{\hspace{2cm}} German.
    \begin{enumerate}[label=\alph*.] \item Know \item Knew \end{enumerate}

    \item I wish I had \underline{\hspace{2cm}} English.
    \begin{enumerate}[label=\alph*.] \item Know \item Known \end{enumerate}

    \item I would \underline{\hspace{2cm}} go home.
    \begin{enumerate}[label=\alph*.] \item Rather \item Prefer \end{enumerate}

    \item I had \underline{\hspace{2cm}} go home.
    \begin{enumerate}[label=\alph*.] \item Best \item Better \end{enumerate}

    \item \underline{\hspace{2cm}} tall is your mother?
    \begin{enumerate}[label=\alph*.] \item What \item How \end{enumerate}

    \item What's the weather \underline{\hspace{2cm}}?
    \begin{enumerate}[label=\alph*.] \item As \item Like \end{enumerate}
\end{enumerate}

\section{IV. TRANSLATION (10 points)}

\subsection{D. Choose the correct translation into Spanish for the following sentences:}

\begin{enumerate}
    \item "The nodes are found to be enlarged"
    \begin{enumerate}[label=\alph*.]
        \item Se encuentra que los nódulos están alargados.
        \item Qué tan alargados los nódulos se encuentran.
        \item Los nódulos parecen estar algo alargados.
    \end{enumerate}

    \item "There may be excess of blood"
    \begin{enumerate}[label=\alph*.]
        \item Allí puede estar el exceso de sangre.
        \item Puede haber exceso de sangre.
        \item Puede estar allí el exceso de sangre.
    \end{enumerate}

    \item "They were known to undergo changes"
    \begin{enumerate}[label=\alph*.]
        \item Eran conocidos por estar sufriendo.
        \item Se conocía que sufrían cambios.
        \item Se conocían por los cambios que estaban sufriendo.
    \end{enumerate}

    \item "There soon follow changes"
    \begin{enumerate}[label=\alph*.]
        \item Los cambios vienen.
        \item Habrá cambios.
        \item Pronto vienen cambios.
    \end{enumerate}

    \item "On exercise the pain became stronger"
    \begin{enumerate}[label=\alph*.]
        \item Durante el ejercicio es más fuerte este que el dolor.
        \item Durante el dolor el ejercicio se hará más fuerte.
        \item Durante el ejercicio el dolor se hace más fuerte.
    \end{enumerate}

    \item "It's work approximates that of the left"
    \begin{enumerate}[label=\alph*.]
        \item Su trabajo al que se aproxima es al que sale de la izquierda.
        \item El que sale de la izquierda es al que se aproxima.
        \item Su trabajo se aproxima al de la izquierda.
    \end{enumerate}

    \item "They estimated the blood leaving the coronary vessels"
    \begin{enumerate}[label=\alph*.]
        \item Calcularon la sangre que deja los vasos coronarios.
        \item Calcularon dejar que los vasos coronarios de ellos sangre.
        \item Los vasos coronarios calcularon la sangre que ellos dejaron.
    \end{enumerate}

    \item "The happier the better"
    \begin{enumerate}[label=\alph*.]
        \item Cuanto más feliz mejor.
        \item Cuanto mayor sea la felicidad mejor.
        \item El más feliz es el mejor.
    \end{enumerate}

    \item "The changes to be considered"
    \begin{enumerate}[label=\alph*.]
        \item Considera cambios al estar.
        \item Los cambios considerados al ser.
        \item Los cambios a considerarse.
    \end{enumerate}

    \item "They develop slowly"
    \begin{enumerate}[label=\alph*.]
        \item El desarrollo es lento.
        \item Lo desarrollan muy lentamente.
        \item Se desarrollan lentamente.
    \end{enumerate}
\end{enumerate}

\vspace{0.5cm}

\section{V. HOMOPHONES (5 points)}

\subsection{E. Fill in the blanks with the correct word. Both options have the same pronunciation but a different meaning.}

\begin{enumerate}
    \item (break / brake) "He managed to stop the car safely using the hand \underline{\hspace{3cm}}."
    \item (great / grate) "Finally, \underline{\hspace{3cm}} some parmesan cheese and put it on your pasta."
    \item (naval / navel) "He comes from a \underline{\hspace{3cm}} family; all his brothers are sailors."
    \item (pain / pane) "If you have a \underline{\hspace{3cm}} in the chest, you should see a doctor."
    \item (paste / paced) "He \underline{\hspace{3cm}} backwards and forwards in front of the door."
\end{enumerate}

\vspace{0.5cm}

\section{VI. VOCABULARY (5 points)}

\subsection{F. Complete the sentences with the appropriate word.}

\begin{enumerate}
    \item I am \underline{\hspace{3cm}} snakes. \\
    She's \underline{\hspace{3cm}} the baby; he doesn't look very well.

    \item Come and sit down \underline{\hspace{3cm}} me. \\
    \underline{\hspace{3cm}} managing the shop, he also teaches in the evening.

    \item The \underline{\hspace{3cm}} brought the Rolls Royce to the hotel's main entrance. \\
    He's got a job as a bus \underline{\hspace{3cm}}.

    \item I haven't seen her \underline{\hspace{3cm}} this morning. \\
    I've \underline{\hspace{3cm}} done my shopping.

    \item Please, can we go home \underline{\hspace{3cm}}? \\
    It looks quite small, but \underline{\hspace{3cm}} it is over 5 metres high.
\end{enumerate}

\section{VII. GENERAL KNOWLEDGE (5 points)}

\subsection{G. Choose the correct answer.}

\begin{enumerate}
    \item "The Teacher Training System" in Spanish is:
    \begin{enumerate}[label=\alph*.]
        \item El sistema del profesor en el entrenamiento.
        \item El sistema de entrenamiento del profesor.
        \item El profesor entrenando el sistema.
        \item El entrenamiento para el sistema del profesor.
    \end{enumerate}

    \item The number: 28.73 is in decimals:
    \begin{enumerate}[label=\alph*.]
        \item Two thousand eight hundred and seventy three hundredths.
        \item Twenty eight and seventy three hundredths.
        \item Twenty eight hundred seventy three decimals.
        \item Two hundred eighty seven and three decimals.
    \end{enumerate}

    \item One metre is equivalent to:
    \begin{enumerate}[label=\alph*.]
        \item 4.08 feet
        \item 3.28 feet
        \item 2.88 feet
        \item 3.65 feet
    \end{enumerate}

    \item An addition connector is:
    \begin{enumerate}[label=\alph*.]
        \item If
        \item First
        \item Furthermore
        \item For example
    \end{enumerate}

    \item A result connector is:
    \begin{enumerate}[label=\alph*.]
        \item Therefore
        \item Unlike
        \item And
        \item In short
    \end{enumerate}

    \item "Carpet" means in Spanish:
    \begin{enumerate}[label=\alph*.]
        \item Alfombra
        \item Carpeta
        \item Carro-mascota
        \item Ninguna de las anteriores
    \end{enumerate}

    \item "No usual" in English is:
    \begin{enumerate}[label=\alph*.]
        \item Inusual
        \item Disusual
        \item Nousual
        \item Unusual
    \end{enumerate}

    \item Albert Einstein wrote this science book:
    \begin{enumerate}[label=\alph*.]
        \item Mathematical Principles
        \item The Cosmic Connection Theory
        \item A Brief History of Time
        \item Relativity General Theory
    \end{enumerate}

    \item Hydrogen is a Gas:
    \begin{enumerate}[label=\alph*.]
        \item Mercury is a Liquid
        \item Oxygen is a Breath
        \item Air is a Life Agent
        \item Steel is a Solid
    \end{enumerate}

    \item El Phrasal Verb de "Admirar" es:
    \begin{enumerate}[label=\alph*.]
        \item Get Up To
        \item Get Along Well
        \item Looking Forward To
        \item Look Up To
    \end{enumerate}
\end{enumerate}

\vspace{0.5cm}

\section{VIII. LISTENING SECTION}

\textit{Listen to the recording while reading the text below. Write the missing words in the blanks.}

\begin{center}
    \textbf{Historic letters get responses}
\end{center}

Many years ago, an old woman named Peggy Ford wrote letters to some men. The men were soldiers \underline{\hspace{2cm}} (1) were fighting in the Vietnam War. The soldiers were in combat, far away from their home. They \underline{\hspace{2cm}} (2) their families, and they liked to get the letters from Peggy. Peggy also kept the letters that the soldiers wrote back to her. Peggy Ford died more than 30 years ago. Earlier this year, Ford’s children \underline{\hspace{2cm}} (3) the letters in her attic. They decided to donate the letters to a history museum. The museum is happy to have the letters. They feel that the \underline{\hspace{2cm}} (4) stories of the war are valuable. They tell the story of the war better than anyone else could. The museum feels that it’s important to remember the war. The letters show a personal perspective of the war. They are a valuable part of history.

A \underline{\hspace{2cm}} (5) station filmed a story about Peggy Ford and the letters. The story was posted on the internet. Many people saw the story, and read about Ford’s letters to the soldiers. The story made other people want to donate their letters. Many people called the museum. They \underline{\hspace{2cm}} (6) to donate their letters from that era. One woman gave the museum more than 200 letters that she wrote to her husband while he was \underline{\hspace{2cm}} (7) in Vietnam. She had \underline{\hspace{2cm}} (8) them for many years. She thought others would be interested in them.

Peggy Ford was a kind, caring woman. Her letters to the soldiers made them feel better. One woman thinks Ford is an inspiration. She is \underline{\hspace{2cm}} (9) others to write to soldiers in Iraq. She says that a letter would bring a smile to a \underline{\hspace{2cm}} (10) face. Cookies and other treats could be sent with the letters. Small gifts and letters would make the soldiers feel better. She plans to write many letters to soldiers, just as Ford did many years ago. She believes that it’s important to say thank you to the soldiers. She thinks the letters would be a good way to do that. She knows that the soldiers appreciate the letters.

\vspace{0.5cm}

\section{IX. COMPOSITION (20 points)}

Choose one of the following topics and write a text of at least 160 words.
\begin{enumerate}
    \item What are your views of English as a global language?
    \item Differences between mother language and foreign language.
    \item What are the advantages of being bilingual?
\end{enumerate}

\vspace{10cm}
\dotfill

\newpage

\section{ANSWER KEY}

\subsection{Section I: Reading Comprehension}
1. c \quad 2. c \quad 3. a \quad 4. c \quad 5. c \quad 6. c \quad 7. a \quad 8. a \quad 9. b \quad 10. c \\
Synonyms: Paw (Hand), Sting (Bite), Banishment (Expulsion), Peacelike (Quiet), Clay (Mud), Whispered (Murmur), Duty (Responsibility), Treason (Betrayal).

\subsection{Section II: HIV Breakthrough}
1. major \quad 2. gap \quad 3. considerable \quad 4. unstable \quad 5. mutate \quad 6. detection \quad 7. However \quad 8. relative \quad 9. blood \quad 10. has \quad 11. rare \quad 12. success.

\subsection{Section III: Grammar}
1. a \quad 2. a \quad 3. a \quad 4. b \quad 5. a \quad 6. a \quad 7. b \quad 8. a \quad 9. a \quad 10. a \\
11. a \quad 12. b \quad 13. a \quad 14. a \quad 15. a \quad 16. b \quad 17. a \quad 18. b \quad 19. b \quad 20. b \\
21. b \quad 22. a \quad 23. a \quad 24. a \quad 25. a \quad 26. b \quad 27. b \quad 28. b \quad 29. a \quad 30. a \\
31. a \quad 32. b \quad 33. b \quad 34. a \quad 35. a \quad 36. b \quad 37. a \quad 38. b \quad 39. b \quad 40. a \\
41. b \quad 42. b \quad 43. a \quad 44. b \quad 45. b \quad 46. b \quad 47. a \quad 48. a \quad 49. b \quad 50. b

\subsection{Section IV: Translation}
1. a \quad 2. b \quad 3. b \quad 4. c \quad 5. c \quad 6. c \quad 7. a \quad 8. a \quad 9. c \quad 10. c

\subsection{Section V: Homophones}
1. brake \quad 2. grate \quad 3. naval \quad 4. pain \quad 5. paced

\subsection{Section VI: Vocabulary}
1. afraid of / worried about \\
2. beside / Besides \\
3. chauffeur / driver \\
4. yet / already \\
5. now / actually

\subsection{Section VII: General Knowledge}
1. b \quad 2. b \quad 3. b \quad 4. c \quad 5. a \quad 6. a \quad 7. d \quad 8. d \quad 9. a \quad 10. d

\subsection{Section VIII: Listening (Peggy Ford)}
1. who \quad 2. missed \quad 3. discovered \quad 4. soldier's \quad 5. near \quad 6. offered \quad 7. stationed \quad 8. saved \quad 9. erguin \quad 10. soldier's

\end{document}
